\chapter{Introduction}
\epigraph{Companies spend millions of dollars on firewalls, encryption, and secure access devices, and it's money wasted because none of these measures address the weakest link in the security chain: the people who use, administer, operate and account for computer systems that contain protected information.}{\textit{Kevin Mitnick}, \\ The Art of Deception: Controlling the Human Element of Security}
\pagenumbering{arabic} \setcounter{page}{1}

\hypertarget{background}{%
\section{Background}\label{background}}

The importance of hardware security has escalated in our increasingly
digital world, where the proliferation of smart devices makes every
aspect of our lives interconnected and, potentially, vulnerable. This
surge in connectivity has broadened the attack surface for malicious
actors, making hardware security a critical pillar of our digital
infrastructure's integrity.

Video game consoles, such as the Nintendo Switch, epitomize the
sophisticated nature of modern hardware. These devices are not merely
platforms for entertainment but intricate ecosystems comprising
proprietary software, custom hardware components, and online services.
They embody a blend of performance, entertainment, and connectivity,
making them a prime target for exploitation.

The Nintendo Switch, in particular, presents an intriguing case study in
hardware security. Its popularity and unique design have attracted
attention not only from millions of users worldwide but also from
individuals and groups looking to exploit potential vulnerabilities for
various purposes, ranging from piracy to the customization of the device
beyond the manufacturer's intended limitations. The discovery of the
Fusee Gelee vulnerability, a significant exploit within the Switch's
boot ROM, highlights the ongoing tension between hardware manufacturers,
who strive to secure their devices, and the hacker community, which
continually seeks to find and exploit vulnerabilities.

To understand the gravity of such exploits, one must consider the
broader implications of hardware vulnerabilities. Unlike software flaws,
which can often be patched through updates, vulnerabilities at the
hardware level can be more challenging to address. They may require
physical recalls or rely on mitigation strategies that can only minimize
the risk rather than eliminate it. The presence of such vulnerabilities
underscores the necessity of robust hardware security measures not only
to protect intellectual property and user data but also to maintain
trust in digital ecosystems.

\hypertarget{thesis-statement}{%
\section{Thesis Statement}\label{thesis-statement}}

The core of this thesis is encapsulated in the exploration of the Fusee
Gelee exploit, a significant vulnerability within the Nintendo Switch's
security architecture. This exploit does not merely represent a singular
flaw within a popular gaming console; it symbolizes the broader
challenges and implications inherent in securing complex hardware
systems in the digital age. The statement of this thesis posits that:

\emph{The detailed examination of the Fusee Gelee exploit serves as a
critical case study, shedding light on the broader issues surrounding
hardware vulnerabilities, their potential impacts on various digital
ecosystems, and the evolving landscape of hardware security measures.}

This statement underscores the exploit's role as a window into
understanding the dynamics between hardware designers and the hacker
community. It emphasizes the need to delve into the technical specifics
of such vulnerabilities to appreciate their severity and potential
ramifications. The analysis of Fusee Gelee is not confined to its
technical execution but extends to understanding its implications on the
security posture of similar devices and systems.

The case of Fusee Gelee is particularly illuminating because it involves
exploiting a vulnerability in the boot ROM of the Nintendo Switch, a
component that is fundamental to the device's operation and, crucially,
cannot be modified once manufactured. This immutability makes mitigating
the exploit particularly challenging and highlights the importance of
foresight and robust security measures in hardware design.

The significance of this exploit---and the reason it is central to this
thesis---is twofold:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Technical Insight}: It provides a deep technical insight into
  the nature of hardware vulnerabilities, particularly those embedded
  deeply within a system's architecture, inaccessible to conventional
  software patches.
\item
  \textbf{Broader Implications}: It prompts a discussion on the broader
  implications for the security of interconnected devices. As devices
  become increasingly complex and integral to personal and professional
  life, understanding and mitigating such vulnerabilities become
  paramount.
\end{enumerate}

In sum, the thesis statement frames the Fusee Gelee exploit as a pivotal
case study for understanding the intricacies of hardware security and
the continuous efforts required to protect against evolving threats.

The primary objectives of this thesis are designed to build a
comprehensive understanding of hardware vulnerabilities, with a
particular focus on the Fusee Gelee exploit within the Nintendo Switch,
and to evaluate mitigation strategies that can be employed against such
vulnerabilities. The objectives are outlined as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Comprehensive Overview of Hardware Vulnerabilities}: To
  conduct a thorough literature review that maps the landscape of
  hardware vulnerabilities, categorizing them based on their nature,
  origin, and impact. This review aims to establish a foundational
  understanding of the challenges in hardware security, setting the
  stage for a deeper exploration of specific exploits like Fusee Gelee.
\item
  \textbf{In-depth Analysis of the Fusee Gelee Exploit}: To dissect the
  Fusee Gelee exploit in detail, examining how it was discovered, its
  technical mechanisms, and how it manages to circumvent the Nintendo
  Switch's security measures. This analysis will provide insights into
  the exploit's workings, offering a case study of how a single
  vulnerability can have significant ramifications.
\item
  \textbf{Assessment of Mitigation Strategies}: To evaluate existing
  strategies employed to mitigate hardware vulnerabilities, focusing on
  their applicability and effectiveness in the context of the Fusee
  Gelee exploit. This will involve an examination of both reactive
  measures taken post-discovery and proactive strategies that can be
  integrated into the design and manufacturing processes to prevent
  similar vulnerabilities.
\end{enumerate}

\hypertarget{detailed-breakdown-of-objectives}{%
\subsection{Detailed Breakdown of
Objectives}\label{detailed-breakdown-of-objectives}}

\begin{itemize}
\item
  \textbf{Objective 1}: The literature review will encompass academic
  papers, security conference proceedings, and industry whitepapers to
  create a taxonomy of hardware vulnerabilities. This will include
  discussions on side-channel attacks, fault injection, hardware
  Trojans, and more, providing a broad perspective on the types of
  challenges faced in securing hardware.
\item
  \textbf{Objective 2}: The analysis of Fusee Gelee will be technical,
  involving an examination of the Tegra X1's boot ROM, the role of the
  BootROM bug, and how the vulnerability is exploited to run arbitrary
  code. It will also cover the implications of such an exploit, from the
  perspective of both security professionals and end-users.
\item
  \textbf{Objective 3}: The assessment will cover specific mitigation
  strategies, such as secure boot, hardware patches, and the use of
  Trusted Execution Environments (TEEs). It will critically analyze the
  effectiveness of Nintendo's responses and general practices in the
  industry for preventing and responding to hardware vulnerabilities.
\end{itemize}

\hypertarget{supporting-concepts-and-tools}{%
\subsection{Supporting Concepts and
Tools}\label{supporting-concepts-and-tools}}

To achieve these objectives, the thesis will leverage various concepts
and tools, including:

\begin{itemize}
\item
  \textbf{Reverse Engineering}: Techniques and tools for reverse
  engineering will be discussed, as they are crucial for uncovering and
  understanding hardware vulnerabilities.
\item
  \textbf{Cryptography}: The role of cryptographic measures in securing
  hardware, particularly in the context of secure boot processes and
  data protection.
\item
  \textbf{Security Frameworks}: Examination of frameworks and standards
  for hardware security, such as the Trusted Computing Group's
  guidelines and the Common Criteria for Information Technology Security
  Evaluation.
\end{itemize}

\hypertarget{scope}{%
\section{Scope}\label{scope}}

While the Fusee Gelee exploit within the Nintendo Switch serves as the
focal point of this thesis, it is crucial to delineate the boundaries of
the discussion to maintain a focused and coherent analysis. The scope of
this thesis includes the points talked about in the Objectives

\hypertarget{limitations}{%
\subsection{Limitations}\label{limitations}}

To ensure a focused analysis, the thesis will not cover:

\begin{itemize}
\item
  \textbf{Software Vulnerabilities}: While recognizing that hardware and
  software security are often intertwined, this thesis will limit its
  discussion to hardware vulnerabilities and the specific intersection
  with software only where relevant to the Fusee Gelee exploit.
\item
  \textbf{Comprehensive Survey of All Hardware Vulnerabilities}: Given
  the vast and evolving nature of hardware vulnerabilities, the thesis
  will not provide an exhaustive survey of all known hardware
  vulnerabilities but will instead highlight those most relevant to the
  context of the Nintendo Switch and similar consumer electronics.
\item
  \textbf{Detailed Technical Solutions}: While mitigation strategies
  will be discussed, the thesis will not delve into the detailed
  technical design of specific security solutions, focusing instead on
  the conceptual and strategic levels.
\end{itemize}

\hypertarget{rationale-for-scope}{%
\subsection{Rationale for Scope}\label{rationale-for-scope}}

The chosen scope ensures that the thesis remains manageable while
providing valuable insights into a significant area of hardware
security. By focusing on the Fusee Gelee exploit, the thesis leverages a
specific, well-documented case to explore broader themes and challenges
in hardware security, making it both relevant and accessible to a wider
audience, including those not deeply versed in hardware engineering.

\hypertarget{implications-of-scope}{%
\subsection{Implications of Scope}\label{implications-of-scope}}

By adhering to this scope, the thesis aims to contribute to the
discourse on hardware security by:

\begin{itemize}
\item
  Providing a detailed case study of a significant exploit, offering
  insights that can inform both academic research and practical security
  measures.
\item
  Highlighting the ongoing challenges in securing hardware against
  increasingly sophisticated exploits, underscoring the need for
  continued innovation and vigilance in hardware design and security
  practices.
\item
  Encouraging a broader discussion on the balance between hardware
  security, functionality, and user freedom, particularly in consumer
  electronics where these factors are in constant tension.
\end{itemize}

This scoped approach allows for a thorough exploration of the chosen
topic while acknowledging the vast and complex nature of hardware
security as a field, thereby setting a clear direction for the research
and analysis that follows.

\hypertarget{structure}{%
\section{Structure}\label{structure}}

The thesis is meticulously organized to navigate through the
complexities of hardware security with a spotlight on the Fusee Gelee
exploit.

In the State of the Art in Hardware Security Flaws chapter, the thesis
delves into the historical context of hardware vulnerabilities,
categorizing common types, discussing their impacts and implications,
and reviewing standard mitigation strategies. This chapter also
spotlights the ongoing challenges in the field and potential research
directions, laying a comprehensive foundation for the focused
exploration of the Fusee Gelee exploit that follows.

The third chapter, dedicated to The Nintendo Switch and the Fusee Gelee
Exploit, explores the security architecture of the Nintendo Switch,
detailing the discovery and technical specifics of the Fusee Gelee
vulnerability and its broader implications for hardware security.

Next chapter would be on methodology and practical analysis, the
subsequent section combines an outline of the research approach and
experimentation ethics with a thorough documentation of replicating the
Fusee Gelee exploit. This includes a detailed account of the
experimental setup, execution, and a critical analysis of the findings,
integrating methodological rigor with practical insights.

Nintendo's Response and Industry Implications is examined next, where
the focus shifts to the countermeasures adopted by Nintendo in response
to the exploit, evaluating their effectiveness and discussing their
broader ramifications for the gaming industry and the domain of hardware
security at large.

The thesis progresses to Alternative Mitigation Strategies, offering a
critical assessment of Nintendo's approach and proposing potential
alternative strategies for addressing similar vulnerabilities,
considering their feasibility, advantages, and limitations.

Concluding the thesis, the Conclusion chapter summarizes the key
findings from the exploration of hardware security issues, the Fusee
Gelee exploit analysis, and the evaluation of mitigation strategies. It
articulates the thesis's contribution to the field of hardware security
and suggests directions for future research.
